---
title: "p8105_hw5_cw3370.Rmd"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(purrr)
library(knitr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

<font size = 5>Describe the raw data</font>
```{r message = FALSE}
homicide_df <- 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") 
```
<font size = 4 face="Times New Roman"> homicide_df includes `r nrow(homicide_df)` observations for `r ncol(homicide_df)` variables. For variables, they are `r colnames(homicide_df)`. 

`r colnames(homicide_df)[1]` is the uid of homicide. 

`r colnames(homicide_df)[2]` is report date of homicide,the format is "yyyymmdd".

`r colnames(homicide_df)[c(3,4)]` is the first name and last name of victim

`r colnames(homicide_df)[c(5,6,7)]` is the race,age,sex of victim

`r colnames(homicide_df)[c(8,9)]` is the location(city state) of homicide

`r colnames(homicide_df)[c(10,11)]`is the specific location(latitude,longtitude) of homicide

`r colnames(homicide_df)[12]` is the deposition of homicide

</font>


<font size = 5>Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).</font>
```{r}
city_homicide_df <- 
  homicide_df %>% 
  mutate(
    city_state = str_c(city,state,sep = ","),
    disposition = case_when(
      disposition == "Closed without arrest"|disposition =="Open/No arrest" ~"unsolved",
      disposition == "Closed by arrest" ~ "solved"
      ) 
    ) %>% 
   filter(
     city_state != "Tulsa,AL"
   ) %>% 
  relocate(city_state)

prop_homicide <- 
  city_homicide_df %>% 
  group_by(city_state,disposition) %>% 
  summarize(
    homicide = n()
  ) %>% 
  ungroup() %>% 
  pivot_wider(
    names_from = disposition,
    values_from = homicide
  ) %>% 
  mutate(
    total = unsolved + solved
  )

```

<font size = 5>For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.</font>
```{r}
prop_baltmore <- 
  prop.test(
    x = pull(filter(prop_homicide,city_state == "Baltimore,MD") ,unsolved), 
    n = pull(filter(prop_homicide,city_state == "Baltimore,MD") ,total)
    )  

prop_baltmore <- 
  prop_baltmore %>% 
  broom::tidy() 
  
estimated_proportion = round(pull(prop_baltmore,estimate),2)
confidence_low  = round(pull(prop_baltmore,conf.low),2)
confidence_high  = round(pull(prop_baltmore,conf.high),2)

```

<font size = 5>Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.</font>
```{r }
prop_test_function <- function(city){
  prop_city <- 
    prop_homicide %>% 
    filter(city_state == city) 
  
  test_score <- 
    prop.test(
        x = prop_city$unsolved,
        n = prop_city$total
      )%>% 
    broom::tidy()
  
  final_score <- 
    tibble(
      estimated_proportion = round(pull(test_score,estimate),2),
      confidence_low  = round(pull(test_score,conf.low),2),
      confidence_high  = round(pull(test_score,conf.high),2)
    )
  
  return(final_score)
}

prop_homicide_test <- 
  prop_homicide %>% 
  mutate(
    test_score = map(prop_homicide$city_state,prop_test_function)
  ) %>% 
  unnest(test_score) %>% 
  mutate(
    city_state = fct_reorder(city_state,-estimated_proportion)
  ) 
```


<font size = 5>Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.</font>
```{r }
prop_homicide_test %>% 
  ggplot() + 
  geom_errorbar(aes(x=city_state, ymin = confidence_low, ymax = confidence_high), width = 0.2, size=1, color = "blue") + 
  geom_point(aes(x =city_state,y = estimated_proportion),size = 1,fill = "white") +
  theme(text = element_text(size=9)) +
  coord_flip() +
  labs(
    title = "Estimates proportion and CIs of the number of unsolved homicides for each city",
    x = "City State",
    y = "Value"
  )


```


# Problem 2
<font size = 5>Start with a dataframe containing all file names; the list.files function will help</font>
```{r}
filename_df <- tibble(
  filenames = list.files("data")
)
```

<font size = 5>Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe</font>
```{r message = FALSE}
read_participant_data <- function(filename){
  filepath <- str_c("data/",filename)
  data = read_csv(filepath)
  return(data)
}

participant_df <- 
  filename_df %>% 
  mutate(
    data = map(filenames,read_participant_data),
    )


```

<font size = 5>Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary</font>
```{r}
participant_df <- 
  participant_df %>% 
  mutate(
    control_arm = substr(filenames,1,3),
    subject_id = substr(filenames,5,6)
    ) %>% 
  relocate(subject_id,control_arm) %>% 
  select(-filenames) %>% 
  unnest(data) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value"
  ) %>% 
  mutate(
    week=as.numeric(week)
  )
  
participant_df %>% 
  head(16) %>% 
  knitr::kable(align = "cccc")
```

<font size = 4 face="Times New Roman"> The table above is part of the result of tidying</font>

<font size = 5>Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.</font>

<font size = 4 face="Times New Roman"> From the spaghetti, we can find that the value in experiment group is relatively larger than the value in control group. Besides that, we can find the value in control group maintained in a  level while the value in experiment group shows a rising trend over time.</font>

```{r}
participant_df %>% 
  ggplot(aes(x = week,y=value,color = subject_id)) +
  geom_point()+
  geom_line()+
  facet_grid(.~control_arm)
```


# Problem 3
```{r}
set.seed(10)
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

<font size = 5>There are two cases to address:

(1)For numeric variables, you should fill in missing values with the mean of non-missing values

(2)For character variables, you should fill in missing values with "virginica"

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.</font>
```{r}
replace_value_function <- function(vector){
    if(is.numeric(vector)){
      replace_value = mean(vector,na.rm=TRUE)
    }else if(is.character(vector)){
      replace_value = "virginica"
    }
  replace_na(vector,replace_value)
}

iris_replaced_df <- 
  iris_with_missing %>% 
  map_df(replace_value_function)
```

<font size = 4 face="Times New Roman">
Some Proof

From two table below, we can find that the NA value has been replaced.

The test of the rule of replacement need to view two dataframe:"iris_with_missing","iris_replaced_df"</font>
```{r}
iris_with_missing %>% 
  is.na() %>% 
  summary()

iris_replaced_df %>% 
  is.na() %>% 
  summary()
```

